\chapter{LOCO pseudo-algorithm}\label{appendix:algo}
The pseudo-algorithm for LOCO fitting is presented in this appendix. For the Python implementation, the GitHub Repository~\cite{locosirius} should be consulted.

\begin{algorithm}[h!]
% \scriptsize
% \footnotesize
\SetAlgoLined
\KwResult{Fitted model, $\chi^2$ at each step}
 Get LOCOInput: measured ORM, $\Delta \theta_x$, $\Delta \theta_y$, $\Delta f_{\mathrm{rf}}$, $\nu_x$, $\nu_y$ and $\sigma_{\mathrm{BPM}}$.\\
 Define LOCOConfig: fit parameters, minimization method, singular values selection, constraints, weights, $n_{\mathrm{steps}}$, $\chi^2_{\mathrm{min}}$, $\chi^2_{\mathrm{step}}$, initial $\lambda$, $\lambda_{\mathrm{min}}$, $\lambda_{\mathrm{max}}$.\\
 Change model tunes to match the measured values.\\
 Obtain initial model ORM.\\
 Calculate or load LOCO jacobian matrix.\\
 Perform SVD and singular values filtering on jacobian matrix to obtain its pseudo-inverse.\\
 Calculate initial reference residue vector $\vec{V}_0$ and $\chi^2_0$.\\
 $n \leftarrow 0$ \\
 \While{$n \leq n_{\mathrm{steps}}$}{
  With $\vec{V}_0$, calculate parameters variations $\Delta \vec{P}$.\\
  Apply $\Delta \vec{P}$ to the model and obtain new ORM. \\
  Calculate new residue vector $\vec{V}$ and $\chi^2$. \\
  \eIf{$\chi^2 > \chi_0^2$ or $\chi^2 < \chi^2_{\mathrm{min}}$}{
  \eIf{$\chi^2 > \chi^2_{\mathrm{min}}$ and LM method}{LM Fail $\leftarrow$ LM Loop().\\
  \If{LM Fail}{Stop}
  }{Stop}
   }{
   \eIf{$\chi_0^2 - \chi^2 < \chi_{\mathrm{step}}^2$}{Stop}{
   Update parameters $\vec{P} \leftarrow \vec{P} + \Delta \vec{P}$.\\
   Update model. \\
   Update references $\vec{V}_0 \leftarrow \vec{V}$ and $\chi^{2}_0 \leftarrow \chi^{2}$.\\
   \If{LM method}{Decrease $\lambda$ and recalculate the jacobian pseudo-inverse}
  }}
  $n \leftarrow n + 1$ \\
 }
 Save output.
 \caption{LOCO pseudo-algorithm}
 \label{algo:loco}
\end{algorithm}

The additional loop for the case of Levenberg-Marquardt minimization algorithm usage in LOCO fitting is presented in the Algorithm 2 below.
\begin{algorithm}[h!]
% \footnotesize
% \scriptsize
\SetAlgoLined
\KwResult{LM Fail}
LM Fail $\leftarrow$ True\\
 \While{$\lambda > \lambda_{\mathrm{min}}$ and $\lambda < \lambda_{\mathrm{max}}$}{
 Increase $\lambda$.\\
  Recalculate the jacobian pseudo-inverse.\\
  Recalculate parameters variations $\Delta \vec{P}$.\\
  Apply $\Delta \vec{P}$ to the model and obtain new ORM. \\
  Calculate new residue vector $\vec{V}$ and $\chi^2$.\\
  \If{$\chi^2 < \chi_0^2$}{
   Update parameters $\vec{P} \leftarrow \vec{P} + \Delta \vec{P}$\\
   Update model \\
   Update references $\vec{V}_0 \leftarrow \vec{V}$ and $\chi^{2}_0 \leftarrow \chi^{2}$\\
   LM Fail $\leftarrow$ False.\\
   Stop.}
 }
 \caption{\gls{lm} Loop pseudo-algorithm}
 \label{algo:lm_loop}
\end{algorithm}